Succinct Representations for Abstract Interpretation

### 2011-11-04 papers/PLDI2012/implicitization.tex
commentaires vraiment en commentaire, compatibilite xelatex

%\newcommand{\MM}[1]{{\color{blue} TODO(MM): #1}}
%\newcommand{\JH}[1]{{\color{teal} TODO(JH): #1}}
%\newcommand{\DM}[1]{{\color{violet} TODO(DM): #1}}
\newcommand{\MM}[1]{}
\newcommand{\JH}[1]{}
\newcommand{\DM}[1]{}

% Pour les commentaires
\usepackage[utf8]{inputenc}

@@

\MM{Maintenant que l'ordre a changé dans l'algo, on peut peut-être
  échanger cette section et la suivante ?}

@@

We experimented with a heuristic
of dynamic construction of the $\sigma_i$ functions, adapted from
\citet{DBLP:conf/pldi/GulwaniZ10}. 
\DM{Cette heuristique, je croyais que c'était nous qui l'avions trouvée,
et qu'elle n'était pas dans Gulwani?}
\JH{Non. Gulwani fait la même chose en un peu plus complique (voir commentaire
suivant)}
\MM{Du coup, la contribution~\ref{contr:disjunctive} devrait être
  affaiblie un peu je suppose. Gulwani fait aussi du SMT-solving ?}
\DM{Non, Gulwani énumère tous les chemins un par un à tous les coups.}
\MM{OK, du coup j'ai ajouté une phrase à la fin de la section pour
  rappeler notre contrib}
For each control point $p_i \in P_R$, we start with one single disjunct
($m_i = 1$) and define $\delta_i = 1$.
$M$ denotes an upper bound on the number of disjuncts per control point.

@@

\begin{figure}[h]
  \begin{center}
    \input{./techniques.tex}
  \end{center} 
  \vspace{-20px}
  \caption{Comparison of the abstract values obtained by classical abstract
  interpretation (S), \emph{Guided Static
  Analysis} (G), \emph{Path-focused} technique (PF), our combined technique
  (G+PF), and its version with disjunctive invariants (DIS).
  The $\subsetneq$ bars gives the percentage of invariants stronger (more precise; smaller with respect to inclusion) with the left-side technique,
$\supsetneq$ the percentage of invariants stronger with the right-side technique,
and ``uncomparable'' gives the percentage of invariants that are uncomparable, i.e
neither greater nor smaller;
the code points where both invariants are equal make up the remaining percentage. See Tab.~\ref{tab:techniques} for details.}
  \label{fig:techniques}
\end {figure}

>>>>

%\newcommand{\MM}[1]{{\color{blue} TODO(MM): #1}}
%\newcommand{\JH}[1]{{\color{teal} TODO(JH): #1}}
%\newcommand{\DM}[1]{{\color{violet} TODO(DM): #1}}
%\newcommand{\MM}[1]{}
%\newcommand{\JH}[1]{}
%\newcommand{\DM}[1]{}

\usepackage{ifxetex}
\ifxetex
\else
\usepackage[utf8]{inputenc}
\fi

@@

%\MM{Maintenant que l'ordre a changé dans l'algo, on peut peut-être
%  échanger cette section et la suivante ?}

@@

We experimented with a heuristic
of dynamic construction of the $\sigma_i$ functions, adapted from
\citet{DBLP:conf/pldi/GulwaniZ10}. 
%\DM{Cette heuristique, je croyais que c'était nous qui l'avions trouvée,
%et qu'elle n'était pas dans Gulwani?}
%\JH{Non. Gulwani fait la même chose en un peu plus complique (voir commentaire
%suivant)}
%\MM{Du coup, la contribution~\ref{contr:disjunctive} devrait être
%  affaiblie un peu je suppose. Gulwani fait aussi du SMT-solving ?}
%\DM{Non, Gulwani énumère tous les chemins un par un à tous les coups.}
%\MM{OK, du coup j'ai ajouté une phrase à la fin de la section pour
%  rappeler notre contrib}
For each control point $p_i \in P_R$, we start with one single disjunct
($m_i = 1$) and define $\delta_i = 1$.
$M$ denotes an upper bound on the number of disjuncts per control point.

@@

\begin{figure}[h]
  \begin{center}
    \input{./techniques.tex}
  \end{center} 
  \vspace{-20pt}
  \caption{Comparison of the abstract values obtained by classical abstract
  interpretation (S), \emph{Guided Static
  Analysis} (G), \emph{Path-focused} technique (PF), our combined technique
  (G+PF), and its version with disjunctive invariants (DIS).
  The $\subsetneq$ bars gives the percentage of invariants stronger (more precise; smaller with respect to inclusion) with the left-side technique,
$\supsetneq$ the percentage of invariants stronger with the right-side technique,
and ``uncomparable'' gives the percentage of invariants that are uncomparable, i.e
neither greater nor smaller;
the code points where both invariants are equal make up the remaining percentage. See Tab.~\ref{tab:techniques} for details.}
  \label{fig:techniques}
\end {figure}
